Location and Scale-Invariant Power Transformations for Transforming Data to

### 2025-12-15 manuscript_rmarkdown/manuscript.Rmd
Grammar and spelling.

- A \textit{dirty} dataset with each sequence drawn from $\mathcal{AGN}\left(\mu = 0, \sigma = 1/\sqrt{2}, \alpha, \beta \right)$,
  with randomly drawn skewness parameter $\alpha \sim U\left(0.01, 0.99\right)$ 
  and shape parameter $\beta \sim U\left(1.00, 5.00 \right)$.
  The sequences are drawn from a range of skewed, unimodal, but not necessarily 
  normal, distributions, to reflect less \textit{clean} data then that presented in the first dataset.

>>>>

- A \textit{dirty} dataset with each sequence drawn from $\mathcal{AGN}\left(\mu = 0, \sigma = 1/\sqrt{2}, \alpha, \beta \right)$,
  with randomly drawn skewness parameter $\alpha \sim U\left(0.01, 0.99\right)$ 
  and shape parameter $\beta \sim U\left(1.00, 5.00 \right)$.
  The sequences are drawn from a range of skewed, unimodal, but not necessarily 
  normal, distributions, to reflect less \textit{clean} data than presented in the first dataset.
